Light versus Dark in Strong Lensing Galaxies: Dark matter halos are rounder than their stars

### 2014-12-15 shapes/paper.tex
added population-synthesis text

{\bf CB. Do we need to add a bit describing the stellar population synthesis modelling? Can maybe Prasenjit write this?}

>>>>

Stellar-mass maps are taken from \cite{2011ApJ...740...97L}.  In that
work, the light of the galaxy images in all available HST bands was
first fitted using using GALFIT \citep{2002AJ....124..266P}, and the
resulting light maps were used to obtain stellar-mass maps using
stellar population synthesis.  The latter assumed a
\cite{2003PASP..115..763C} IMF and the stellar-population models of
\cite{2003MNRAS.344.1000B}.  A more bottom-heavy IMF would change the
mass normalisation \citep[cf.][]{2014ApJ...793...96S} but not the
inferred shape of the stellar mass.
